Perturbing SU($n$)-symmetric interactions

### 2020-03-05 collective_sun/sun_perturbation.tex
a bit of cleanup of the multi-body eigenvalue problem with TI

We now consider the full $M$-body product
\begin{align}
  H_0 \V_M \ket\psi
  = \sum_{\substack{\p{p,q}\in\C_N\p{2}\\k\in\C_N\p{M}}} h_{pq} w_k
  \Pi_{pq} O_k \ket\psi,
  \label{eq:H_VM_psi_start}
\end{align}
where without loss of generality we consider an $M$-body perturbation
$\V_M$ built out of only one $M$-spin operator $O$.  The sum in
\eqref{eq:H_VM_psi_start} has terms with $p,q\in k$, terms with
$p,q\notin k$, and terms with only one of $p$ or $q\in k$.  The
permutation operator $\Pi_{pq}$ acts trivially on $O_k\ket\psi$ when
$p,q\in k$ or $p,q\notin k$, leaving terms at each fixed $k$ of the
form
\begin{align}
  \sum_{\substack{\p{p,q}\in\C_N\p{2}\\p,q\in k~\t{or}~p,q\notin k}} h_{pq}
  = \sum_{\p{p,q}\in\C_N\p{2}} h_{pq}
  - \sum_{p\in k} \sum_{\substack{q\in\ZZ_N\\q\notin k}} h_{pq}
  = E_0 - \sum_{p\in k}
  \p{\sum_{q\in\ZZ_N} h_{pq} - \sum_{q\in k} h_{pq}},
\end{align}
where we first split a sum over $\p{p,q}\in\C_N\p{2}$ with the
restriction that $p,q\in k~\t{or}~p,q\notin k$ into an unrestricted
sum minus a remainder, and then similarly split the sum over all spins
$q$ with the restriction that $q\notin k$ into a sum over all $q$
minus the remainder $q\in k$.  We thus find that
\begin{align}
  \sum_{\substack{\p{p,q}\in\C_N\p{2}\\p,q\in k~\t{or}~p,q\notin k}} h_{pq}
  = E_0 - \bar h_k,
  &&
  \bar h_k \equiv \sum_{p\in k}\p{h_p - \sum_{q\in k}h_{pq}},
  &&
  h_p \equiv \sum_q h_{pq},
\end{align}
which implies that the terms in \eqref{eq:H_VM_psi_start} with
$p,q\in k$ or $p,q\notin k$ are
\begin{align}
  \sum_{k\in\C_N\p{M}} \p{E_0 - \bar h_k} w_k O_k \ket\psi
  = E_0 \V_M \ket\psi
  - \sum_{k\in\C_N\p{M}} \p{\bar{\m h} * \m w}_k O_k \ket\psi,
\end{align}
where $\bar{\m h}$ is a tensor with entries $\bar h_k$; and
$\m x*\m y$ denotes an element-wise (Kronecker) product of $\m x$ and
$\m y$, with entries $x_ky_k$.

The remaining terms in \eqref{eq:H_VM_psi_start} with only one of
$p\in k$ or $q\in k$ are
\begin{align}
  \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{q\in k}
  h_{pq} w_k \Pi_{pq} O_k \ket\psi
  = \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \sum_{j=1}^M h_{p k_j} w_k \Pi_{p k_j} O_k \ket\psi.
\end{align}
Defining
$k_{jp}\equiv\p{k_1,k_2,\cdots,k_{j-1},p,k_{j+1},\cdots,k_M}$, i.e.~an
element of $\C_N\p{M}$ in which the $j$-th number $k_j$ has been
replaced by $p$, we can simplify
\begin{align}
  \Pi_{p k_j} O_k \ket\psi
  = \Pi_{p k_j} O_k \Pi_{p k_j} \ket\psi
  = O_{k_{jp}}\ket\psi,
\end{align}
and switch the labels for $p$ and $k_j$ to find that
\begin{align}
  \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{q\in k}
  h_{pq} w_k  \Pi_{pq} O_k \ket\psi
  = \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \sum_{j=1}^M h_{pk_j} w_{k_{jp}} O_k \ket\psi.
\end{align}
For each fixed $j$, the sum over $p$ above is essentially a
contraction of the matrix $\m h$ with the $j$-th index of the tensor
$\m w$.  Denoting such a contraction by $\m h\c_j\m w$, we can
therefore write this result as
\begin{align}
  \sum_{k\in\C_N\p{M}} \p{\m h\circ \m w}_k O_k \ket\psi,
  &&
  \m h\circ\m w \equiv \sum_{j=1}^M \m h\c_j\m w,
\end{align}
where, for clarity, the matrix elements of $\m h\circ\m w$ are
\begin{align}
  \p{\m h\circ\m w}_k
  \equiv \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{j=1}^M
  h_{pk_j} w_{k_{jp}}
  = \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \p{h_{k_1 p} w_{pk_2k_3\cdots k_M}
    + h_{k_2 p} w_{k_1pk_3\cdots k_M}
    + \cdots + h_{k_M p} w_{k_1k_2\cdots k_{M-1} p}}.
\end{align}
Altogether, we thus find that
\begin{align}
  H_0 \V_M \ket\psi
  = E_0 \V_M \ket\psi + \sum_{k\in\C_N\p{M}}
  \p{\m h\circ\m w - \bar{\m h} * \m w}_k O_k \ket\psi.
  \label{eq:H_VM_psi_end}
\end{align}
The action of the $M$-body perturbation $\V_M$ on a fully symmetric
state therefore generates an eigenstate of $H_0$ with energy
$E_0+\Delta$ if the coefficient tensor $\m w$ satisfies the
generalized eigenvalue equation
\begin{align}
  \m h\circ\m w - \bar{\m h} * \m w = \Delta \m w.
  \label{eq:H_VM_psi_eig}
\end{align}
If $M=1$, then $\p{\m h\circ\m w}_k=\sum_\ell h_{k\ell}w_\ell$ and
$\bar h_k=h_k$, so
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi + \sum_{k\in\ZZ_N}
  \p{\sum_{\ell\in\ZZ_N} h_{k\ell} w_\ell - h_k w_k} O_k \ket\psi,
\end{align}
which is precisely what we found in \eqref{eq:H_V1_psi_end}.  If
$M=2$, then
$\p{\m h\circ\m w}_{pq}=\sum_k\p{h_{pk}w_{kq}+h_{qk}w_{pk}}$, so
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi + \sum_{\p{p,q}\in\C_N\p{2}}
  \sp{\sum_{k\in\ZZ_N}\p{h_{pk} w_{kq} + h_{qk} w_{pk}}
    - \bar h_{pq} w_{pq}}
  O_k \ket\psi,
\end{align}
where $\bar h_{pq}=h_p+h_q-2h_{pq}$ with $h_p\equiv\sum_qh_{pq}$.

@@

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys both permutational
symmetry and translational invariance.  To this end, we first expand
the coupling tensor $\m w$ in a complete basis for all tensors of
dimension $M$:
\begin{align}
  \m w = \sum_{k\in\ZZ_N^M} w_k \m e_k,
\end{align}
where $\m e_k$ is a unit tensor with one in the entry indexed by $k$
and zeros everywhere else.  We then use the permutational symmetry of
$\m w$ to expand it in a basis for symmetric tensors, making use of
the fact that all entries of $\m w$ with repeated indices are zero:
\begin{align}
  \m w = \sum_{k\in\C_N\p{M}} w_k \m m_k,
  &&
  \m m_k \equiv \sum_{\sigma\in P_M} \m e_{\sigma\p{k}},
  \label{eq:sym_tensor}
\end{align}
where $P_M$ is the set of all permutations of $M$ symbols.  On a
$D$-dimensional lattice of linear size $L$, translational invariance
implies that the coefficients $w_k$ remain the same if all spins
indexed by $k$ are shifted by the same displacement $d\in\ZZ_L^D$.  To
account for this invariance, we denote a translation of all spins in
$k$ by a displacement $d\in\ZZ_L^D$ by $k_d$, and define the
translation-symmetrized basis tensors
\begin{align}
  \m m_k^{\t{TS}}
  \equiv \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \m m_{k_d}
  = \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \sum_{\sigma\in P_M}
  \m e_{\sigma(k_d)},
\end{align}
where the normalization factor $\N_k^{\t{TS}}$ enforces that the
entries of $\m m_k^{\t{TS}}$ are all either zero or one, which
otherwise might not occur if some translations of $k$ results in the
same choice of spins.  We then define the set $\T_N\p{M}$ of
equivalence classes in $\C_N\p{M}$ under arbitrary translations, and
expand
\begin{align}
  \m w = \sum_{k\in\T_N\p{M}} w_k \m m_k^{\t{TS}}.
  \label{eq:sym_shift_tensor}
\end{align}
Having expanded $\m w$ in a basis that respects permutational symmetry
and translational invariance, we need to express the eigenvalue
equation \eqref{eq:H_VM_psi_eig} in the same basis.  In order to do
so, we label spins $p,q$ by the position of the corresponding lattice
site in $\ZZ_L^D$, and use translational invariance of the couplings
$\m h$ to expand
\begin{align}
  \m h \equiv \sum_{p,q\in\ZZ_L^D} h_{pq} \op{p}{q}
  = \sum_{q,d\in\ZZ_L^D} h_{q+d,q} \op{q+d}{q}
  = \sum_{d\in\ZZ_L^D} h_{d,0} \m s_d,
  &&
  \m s_d \equiv \sum_{q\in\ZZ_L^D} \op{q+d}{d}.
\end{align}
Starting from this form of $\m h$ and the expansion of $\m w$ in
\eqref{eq:sym_tensor}, we can work out that
\begin{align}
  \m h\circ\m w
  = \sum_{k\in\T_N\p{M}} \m m_k^{\t{TS}}
  \sum_{d\in\ZZ_L^D} h_{d,0} \sum_{a=1}^M w_{k_{d;a}},
\end{align}
where $k_{d;a}$ denotes the spins acquired by displacing the $a$-th
spin of $k$ by $d$.  With a bit of additional work, we can also
simplify
\begin{align}
  \bar{\m h} * \m w = M h_0 \m w
  - \sum_{k\in\T_N\p{M}} w_k \m m_k^{\t{TS}}
  \sum_{p,q\in k} h_{pq}
  &&
  h_0 \equiv \sum_{d\in\ZZ_L^D} h_{d,0}.
\end{align}
Putting everything together, the generalized eigenvalue problem in
\eqref{eq:H_VM_psi_eig} can be written in the form
\begin{align}
  \sum_{k\in\T_N\p{M}} \m m_k^{\t{TS}}
  \sp{\sum_{p,q\in k} h_{pq} w_k
    + \sum_{d\in\ZZ_L^D} h_{d,0} \sum_{a=1}^M w_{k_{d;a}}}
  = \p{M h_0 + \Delta} \m w,
\end{align}
or equivalently
\begin{align}
  \ut{\check{\m h}} \c \v{\m w} = \p{M h_0 + \Delta} \v{\m w},
  \label{eq:H_VM_eig_simp}
\end{align}
where
\begin{align}
  \ut{\check{\m h}} \equiv
  \sum_{k\in\T_N\p{M}} \ket{k}
  \sp{\sum_{p,q\in k} h_{pq} \bra{k}
    + \sum_{d\in\ZZ_L^D} h_{d,0} \sum_{a=1}^M \bra{k_{d;a}}},
  &&
  \v{\m w} \equiv \sum_{k\in\T_N\p{M}} w_k \ket{k},
\end{align}
and, to keep notation simple, we define $\ket{k}=0$ for all $k$ with
repeated values, and enforce $\ket{j}=\ket{k}$ if spins $j$ and spins
$k$ are the same up to a global translation.

\vspace{1cm}

\red{TODO: write codes to check above work, fix any errors, explicitly
  write out two-body reduced eigenvalue problems, include sub-section
  about isotropy, replace the following appendix}

\vspace{1cm}

>>>>

We now consider the full $M$-body product
\begin{align}
  H_0 \V_M \ket\psi
  = \sum_{\substack{\p{p,q}\in\C_N\p{2}\\k\in\C_N\p{M}}} h_{pq} w_k
  \Pi_{pq} O_k \ket\psi,
  \label{eq:H_VM_psi_start}
\end{align}
where without loss of generality we consider an $M$-body perturbation
$\V_M$ built out of only one $M$-spin operator $O$.  The sum in
\eqref{eq:H_VM_psi_start} has terms with $p,q\in k$, terms with
$p,q\notin k$, and terms with only one of $p$ or $q\in k$.  The
permutation operator $\Pi_{pq}$ acts trivially on $O_k\ket\psi$ when
$p,q\in k$ or $p,q\notin k$, leaving terms at each fixed $k$ of the
form
\begin{align}
  \sum_{\substack{\p{p,q}\in\C_N\p{2}\\p,q\in k~\t{or}~p,q\notin k}} h_{pq}
  = \sum_{\p{p,q}\in\C_N\p{2}} h_{pq}
  - \sum_{p\in k} \sum_{\substack{q\in\ZZ_N\\q\notin k}} h_{pq}
  = E_0 - \sum_{p\in k}
  \p{\sum_{q\in\ZZ_N} h_{pq} - \sum_{q\in k} h_{pq}},
\end{align}
where we first split a sum over $\p{p,q}\in\C_N\p{2}$ with the
restriction that $p,q\in k~\t{or}~p,q\notin k$ into an unrestricted
sum minus a remainder, and then similarly split the sum over all spins
$q$ with the restriction that $q\notin k$ into a sum over all $q$
minus the remainder $q\in k$.  We thus find that
\begin{align}
  \sum_{\substack{\p{p,q}\in\C_N\p{2}\\p,q\in k~\t{or}~p,q\notin k}} h_{pq}
  = E_0 - \bar h_k,
  &&
  \bar h_k \equiv \sum_{p\in k}\p{h_p - \sum_{q\in k}h_{pq}},
  &&
  h_p \equiv \sum_q h_{pq},
\end{align}
which implies that the terms in \eqref{eq:H_VM_psi_start} with
$p,q\in k$ or $p,q\notin k$ are
\begin{align}
  \sum_{k\in\C_N\p{M}} \p{E_0 - \bar h_k} w_k O_k \ket\psi
  = E_0 \V_M \ket\psi
  - \sum_{k\in\C_N\p{M}} \p{\bar{\m h} * \m w}_k O_k \ket\psi,
\end{align}
where $\bar{\m h}$ is a tensor with entries $\bar h_k$; and
$\m x*\m y$ denotes an element-wise (Kronecker) product of $\m x$ and
$\m y$, with entries $x_ky_k$.  The remaining terms in
\eqref{eq:H_VM_psi_start} with only one of $p\in k$ or $q\in k$ are
\begin{align}
  \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{q\in k}
  h_{pq} w_k \Pi_{pq} O_k \ket\psi
  = \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \sum_{a=1}^M h_{p k_a} w_k \Pi_{p k_a} O_k \ket\psi.
\end{align}
where $k\equiv\p{k_1,k_2,\cdots,k_M}$, with $k_a$ the $a$-th entry in
$k$.  Defining
$k_{ap}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$, i.e.~an
element of $\C_N\p{M}$ in which the $a$-th number $k_a$ has been
replaced by $p$, we can simplify
\begin{align}
  \Pi_{p k_a} O_k \ket\psi
  = \Pi_{p k_a} O_k \Pi_{p k_a} \ket\psi
  = O_{k_{ap}}\ket\psi,
\end{align}
and switch the labels for $p$ and $k_a$ to find that
\begin{align}
  \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{q\in k}
  h_{pq} w_k  \Pi_{pq} O_k \ket\psi
  = \sum_{k\in\C_N\p{M}} \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \sum_{a=1}^M h_{pk_a} w_{k_{ap}} O_k \ket\psi.
\end{align}
For each fixed $a$, the sum over $p$ above is essentially a
contraction of the matrix $\m h$ with the $a$-th index of the tensor
$\m w$.  Denoting such a contraction by $\m h\c_a\m w$, we can
therefore write this result as
\begin{align}
  \sum_{k\in\C_N\p{M}} \p{\m h\circ \m w}_k O_k \ket\psi,
  &&
  \m h\circ\m w \equiv \sum_{a=1}^M \m h\c_a\m w,
\end{align}
where, for clarity, the matrix elements of $\m h\circ\m w$ are
\begin{align}
  \p{\m h\circ\m w}_k
  \equiv \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a=1}^M
  h_{pk_a} w_{k_{ap}}
  = \sum_{\substack{p\in\ZZ_N\\p\notin k}}
  \p{h_{k_1 p} w_{pk_2k_3\cdots k_M}
    + h_{k_2 p} w_{k_1pk_3\cdots k_M}
    + \cdots + h_{k_M p} w_{k_1k_2\cdots k_{M-1} p}}.
\end{align}
Altogether, we thus find that
\begin{align}
  H_0 \V_M \ket\psi
  = E_0 \V_M \ket\psi + \sum_{k\in\C_N\p{M}}
  \p{\m h\circ\m w - \bar{\m h} * \m w}_k O_k \ket\psi.
  \label{eq:H_VM_psi_end}
\end{align}
The action of the $M$-body perturbation $\V_M$ on a fully symmetric
state therefore generates an eigenstate of $H_0$ with energy
$E_0+\Delta$ if the coefficient tensor $\m w$ satisfies the
generalized eigenvalue equation
\begin{align}
  \m h\circ\m w - \bar{\m h} * \m w = \Delta \m w.
  \label{eq:H_VM_psi_eig}
\end{align}
If $M=1$, then $\p{\m h\circ\m w}_k=\sum_\ell h_{k\ell}w_\ell$ and
$\bar h_k=h_k$, so
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi + \sum_{k\in\ZZ_N}
  \p{\sum_{\ell\in\ZZ_N} h_{k\ell} w_\ell - h_k w_k} O_k \ket\psi,
\end{align}
which is precisely what we found in \eqref{eq:H_V1_psi_end}.  If
$M=2$, then
$\p{\m h\circ\m w}_{pq}=\sum_k\p{h_{pk}w_{kq}+h_{qk}w_{pk}}$, so
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi + \sum_{\p{p,q}\in\C_N\p{2}}
  \sp{\sum_{k\in\ZZ_N}\p{h_{pk} w_{kq} + h_{qk} w_{pk}}
    - \bar h_{pq} w_{pq}}
  O_k \ket\psi,
\end{align}
where $\bar h_{pq}=h_p+h_q-2h_{pq}$ with $h_p\equiv\sum_qh_{pq}$.

@@

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys both permutational
symmetry and translational invariance.  To this end, we first expand
the coupling tensor $\m w$ in a complete basis for symmetric tensors:
\begin{align}
  \m w = \sum_{k\in\C_N\p{M}} w_k \m m_k,
  &&
  \m m_k \equiv \sum_{\sigma\in P_M} \m e_{\sigma\p{k}},
  \label{eq:sym_tensor}
\end{align}
where $P_M$ is the set of all permutations of $M$ symbols, and
$\m e_\ell$ is a unit tensor with one in the entry indexed by $\ell$
and zeros everywhere else.  On a $D$-dimensional lattice of linear
size $L$, translational invariance implies that the coefficients $w_k$
remain the same if all spins indexed by $k$ are shifted by the same
displacement $d\in\ZZ_L^D$.  To account for this invariance, we denote
a translation of all spins in $k$ by a displacement $d\in\ZZ_L^D$ by
$k_d$, and define the translation-symmetrized basis tensors
\begin{align}
  \m m_k^{\t{TS}}
  \equiv \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \m m_{k_d}
  = \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \sum_{\sigma\in P_M}
  \m e_{\sigma(k_d)},
\end{align}
where the normalization factor $\N_k^{\t{TS}}$ enforces that the
entries of $\m m_k^{\t{TS}}$ are all either zero or one, which
otherwise might not occur if some translations of $k$ results in the
same choice of spins.  We then define the set $\T_{LD}\p{M}$ of
equivalence classes in $\C_N\p{M}$ under arbitrary translations on
$D$-dimensional lattice of linear size $L$, and expand
\begin{align}
  \m w = \sum_{k\in\T_{LD}\p{M}} w_k \m m_k^{\t{TS}}.
  \label{eq:sym_shift_tensor}
\end{align}
Having expanded $\m w$ in a basis that respects permutational symmetry
and translational invariance, we need to express the eigenvalue
equation \eqref{eq:H_VM_psi_eig} in the same basis.  In order to do
so, we label spins $p,q$ by the position of the corresponding lattice
site in $\ZZ_L^D$, and use translational invariance of the couplings
$\m h$ to expand
\begin{align}
  \m h \equiv \sum_{p,q\in\ZZ_L^D} h_{pq} \op{p}{q}
  = \sum_{q,d\in\ZZ_L^D} h_{q+d,q} \op{q+d}{q}
  = \sum_{d\in\ZZ_L^D} h_{d,0} \m s_d,
  &&
  \m s_d \equiv \sum_{q\in\ZZ_L^D} \op{q+d}{d}.
\end{align}
Starting from this form of $\m h$ and the expansion of $\m w$ in
\eqref{eq:sym_tensor}, we can work out that
\begin{align}
  \m h\circ\m w
  = \sum_{k\in\T_{LD}\p{M}} \sum_{d\in\ZZ_L^D} \sum_{a=1}^M w_{k_{d;a}}
  h_{d,0} w_{k_{d;a}} \m m_k^{\t{TS}},
\end{align}
where $k_{d;a}$ denotes the spins acquired by displacing the $a$-th
spin of $k$ by $d$.  With a bit of additional work, we can also
simplify
\begin{align}
  \bar{\m h}
  = \sum_{k\in\T_{LD}\p{M}} \sp{M h_0 - \sum_{p,q\in k} h_{pq}}
  \m m_k^{\t{TS}},
  &&
  h_0 \equiv \sum_{d\in\ZZ_L^D} h_{d,0},
\end{align}
which implies that
\begin{align}
  \bar{\m h} * \m w = M h_0 \m w
  - \sum_{k\in\T_{LD}\p{M}} \sum_{p,q\in k} h_{pq} w_k \m m_k^{\t{TS}}.
\end{align}
Putting everything together, the generalized eigenvalue problem in
\eqref{eq:H_VM_psi_eig} can be written in the form
\begin{align}
  \sum_{k\in\T_{LD}\p{M}} \sp{\sum_{p,q\in k} h_{pq} w_k
    + \sum_{d\in\ZZ_L^D} h_{d,0} \sum_{a=1}^M w_{k_{d;a}}}
  \m m_k^{\t{TS}}
  = \p{M h_0 + \Delta} \m w,
\end{align}
or equivalently
\begin{align}
  \ut{\check{\m h}} \c \v{\m w} = \p{M h_0 + \Delta} \v{\m w},
  \label{eq:H_VM_eig_simp}
\end{align}
where
\begin{align}
  \ut{\check{\m h}} \equiv
  \sum_{k\in\T_{LD}\p{M}} \ket{k}
  \sp{\sum_{p,q\in k} h_{pq} \bra{k}
    + \sum_{d\in\ZZ_L^D} h_{d,0} \sum_{a=1}^M \bra{k_{d;a}}},
  &&
  \v{\m w} \equiv \sum_{k\in\T_{LD}\p{M}} w_k \ket{k},
\end{align}
and, to keep notation simple, we define $\ket{k}=0$ for all $k$ with
repeated values, and enforce $\ket{j}=\ket{k}$ if spins $j$ and spins
$k$ are the same up to a global translation.
